I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-15 Paper/introduction.tex

In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers. This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy}\dots

>>>>

In the past 15 years, Deep Learning has revolutionized many tasks which were thought to be very hard to be handled by computers. This revolution however poses new challenges, as its automatically obtained product, namely Deep Neural Networks (DNNs), does not come with guidelines or rational : it has tens of thousands of parameters (even for shallow networks with hundreds of neurons), it is very hard to understand, it is brittle to small perturbations \cite{Szegedy2013}\dots
